---
title: "Untitled"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

8. This question involves the use of simple linear regression on the Auto data set.
  (a) Use the lm() function to perform a simple linear regression with mpg as the response and horsepower as the predictor. Use the summary() function to print the results. Comment on the output. For example:
    i. Is there a relationship between the predictor and the response? 
```{r cars}
library(ISLR)
data(Auto)
lm.fit=lm(mpg ~ horsepower,data=Auto)
summary(lm.fit)
```
##p-value : <2e-16 ,我們可以顯著認為horsepower跟mpg有關係



  
  ii. How strong is the relationship between the predictor and the response? 
    
    
## R-squared : 0.6059 代表用這個回歸模型mpg可以被horsepower解釋的變異有60.59%
  
  iii. Is the relationship between the predictor and the response positive or negative?
    
##horsepower的係數是-0.157845,所以prefictor和response的關係是負的

  
  
  iv. What is the predicted mpg associated with a horsepower of 98? What are the associated 95% conﬁdence and prediction intervals? 
```{r}
predict(lm.fit, data.frame(horsepower = 98), interval = "prediction")
predict(lm.fit, data.frame(horsepower = 98), interval = "confidence")

```

(b) Plot the response and the predictor. Use the abline() function to display the least squares regression line.
```{r}
attach(Auto)
plot(horsepower,mpg)
abline(lm.fit,col="red")
```
 
 
 
 
  (c) Use the plot() function to produce diagnostic plots of the least squares regression ﬁt. Comment on any problems you see with the ﬁt
```{r}
par(mfrow=c(2,2))
plot(lm.fit)
```

(1)從Residuals vs Fitted 圖中可以看出predictors和response有一點非線性的趨勢
(2)從Normal Q-Q 圖中得知殘差大致符合標準常態分佈
(3)從Scale-Location圖中大致得知取線周圍的點應該隨機分布,而圖中有一些點有微outliers的趨勢

```{r}

```

